---
title: "ADA Final Project Data Cleaning"
author: "Mikayla Branz and Romario Smith"
date: "10/29/2020"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
    code_folding: "hide"
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE, message =FALSE, warning = FALSE)
```
# Bring in Data
Set up data frame:

- Import data from multiple CSV files
- Combine into one data frame
- Trim to remove extraneous variables
- Select only children 72 months and younger
```{r, import data, eval = FALSE}
#Install necessary packages 
pacman::p_load(readr,tidyverse, foreign, ggplot2, poliscidata, survey, MASS, funModeling, brant, dplyr, table1, car, DiagrammeR) 

#Set Working Directory
#setwd("C:/Users/Mikayla Branz/Documents/Grad School Work/Semester 5 Coursework/Advanced Data Analysis/Final Project")

#Use foreign to import .sav files. 
DHSload <- read.spss("ZAIR71FL.sav", use.value.label=TRUE, to.data.frame=TRUE)

#Select relevant variables:
DHS <- DHSload %>% 
dplyr::select(V781, V826A, V025, V012, V106, V190, V501, V208, V836, V525, V763A, V312, V394, V120, V121, V169A, V171A, V021, V022, V005)

#Verify
names(DHS)

#Rename variables
DHS <- DHS %>% 
  rename("HIVTest_Ever" = "V781", 
         "HIVTest_MonthsAgo" = "V826A", 
         "ResidenceType" = "V025", 
         "Age" = "V012", 
         "Education" = "V106", 
         "WealthIndex" = "V190",  
         "MaritalStatus" = "V501", 
         "Births_Last5Years" = "V208",  
         "SexPartners_Lifetime" ="V836",
         "FirstSex_Age" = "V525", 
         "STI_12Months" = "V763A", 
         "ContraceptiveMethod_Current" = "V312", 
         "HealthFacility_12Months" = "V394", 
         "Radio" = "V120", 
         "TV" = "V121", 
         "MobilePhone" = "V169A", 
         "InternetUse" = "V171A", 
         "Cluster" = "V021", 
         "Stratum" = "V022", 
         "Individual_Weight" = "V005")

#Select only women ages 15-24
DHS<-DHS %>%
  filter(Age >= 15 & Age<=24)
```

# Recode Exposure Variable: Residence Type
```{r}
#Check variable type
class(DHS$ResidenceType)

#Check distribution
summary(DHS$ResidenceType)

#Check for missing data
sum(is.na(DHS$ResidenceType))
#No missing values

#Reorder
DHS$ResidenceType<- factor(DHS$ResidenceType, levels = c("Rural", "Urban"))
```
# Recode Outcome Variable: HIV Testing Uptake
```{r}
#Check to ensure that people who never got an HIV test (HIVTest_Ever=0) did not report a number of Months on HIVTest_MonthsAgo. 
table(DHS$HIVTest_Ever, DHS$HIVTest_MonthsAgo)
#It looks consistent. No one in the "Don't know" category. 

#Recode HIV Testing uptake as Yes/No for within the last year. 

#Recode "2 or more years" as 25 so it will be easier to make into categories
DHS$HIVTest_MonthsAgo<-recode_factor(DHS$HIVTest_MonthsAgo,
                                     "Two or more years" = "25")

#Make HIV_MonthsAgo numeric so case_when can handle it
DHS$HIVTest_MonthsAgo<- as.numeric(DHS$HIVTest_MonthsAgo)
  
#Make categorical HIV test variable
DHS <- DHS %>% 
   mutate(HIVTest_LastYear = ifelse(HIVTest_Ever == "Yes" & HIVTest_MonthsAgo <12, "Yes", "No")) 

sum(is.na(DHS$HIVTest_LastYear))                                

#Make factor variable and check that it categorized variables correctly
DHS$HIVTest_LastYear<-as.factor(DHS$HIVTest_LastYear)
levels(DHS$HIVTest_LastYear)
DHS$HIVTest_MonthsAgo<- as.factor(DHS$HIVTest_MonthsAgo)
table(DHS$HIVTest_LastYear, DHS$HIVTest_MonthsAgo)
table(DHS$HIVTest_LastYear, DHS$HIVTest_Ever)
#Looks good!

```
# Fix other variables
## Age
```{r}
#Check missing values for Age variable
sum(is.na(DHS$Age))
#no missing values

#Check class for Age variable
class(DHS$Age)
#Numeric- Looks good!

DHS <- DHS %>% 
   mutate(Age_Cat = case_when(Age < 18 ~ "15-17", 
                              Age <21 & Age >=18 ~ "18-21", 
                              Age <=24 & Age >=21 ~ "21-24"))

class(DHS$Age_Cat)
#make factor variable
DHS$Age_Cat<-as.factor(DHS$Age_Cat)
#Summarize age variable
summary(DHS$Age_Cat)
```
## Education
```{r}
#Check missing values for education variable
sum(is.na(DHS$Education))
#no missing values

#Check class and levels for education variable
class(DHS$Education)
levels(DHS$Education)
summary(DHS$Education)

#Re-arrange into fewer categories
DHS <- DHS %>% 
   mutate(Education_Cat = case_when
                               (Education == "No education"
                                 | Education == "Primary" ~ "None or Primary",
                                Education == "Secondary" ~ "Secondary",
                               Education == "Higher" ~ "Higher"))

table(DHS$Education,DHS$Education_Cat)
#Looks good!

#Re-order levels
levels(DHS$Education_Cat)
 DHS$Education_Cat <- factor(DHS$Education_Cat, levels = c("None or Primary", "Secondary", "Higher"))
```
## Wealth Index
```{r}
#Check missing values for wealth variable
sum(is.na(DHS$WealthIndex))
#no missing values

#Check class and levels for wealth variable
class(DHS$WealthIndex)
levels(DHS$WealthIndex)
summary(DHS$WealthIndex)

#Re-arrange into fewer categories
 DHS <- DHS %>% 
   mutate(WealthIndex_Cat = case_when
                               (WealthIndex == "Poorest"
                                 | WealthIndex == "Poorer" ~ "Poor",
                              WealthIndex == "Middle" ~ "Middle",
                              WealthIndex == "Richer" |  
                              WealthIndex == "Richest" ~ "Rich"))

table(DHS$WealthIndex,DHS$WealthIndex_Cat)
#Looks good!

#Re-order levels
levels(DHS$WealthIndex_Cat)
 DHS$WealthIndex_Cat <- factor(DHS$WealthIndex_Cat, levels = c("Poor", "Middle", "Rich"))
```
## Marital Status
```{r}
#Check missing values for marital status variable
sum(is.na(DHS$MaritalStatus))
#no missing values

#Check class and levels for marital status variable
class(DHS$MaritalStatus)
levels(DHS$MaritalStatus)
summary(DHS$MaritalStatus)
#Looks good!

#Recategorize into fewer categories
DHS <- DHS %>% 
   mutate(MaritalStatus_Cat = case_when
                               (MaritalStatus == "Never in union" ~ "Never in union",
                                MaritalStatus == "Married" 
                                 | MaritalStatus == "Living with partner" ~ "Partnered",
                               MaritalStatus == "Widowed"
                                 | MaritalStatus == "Divorced"
                                 | MaritalStatus == "No longer living together/separated" ~ "Not partnered"))
                             
DHS$MaritalStatus_Cat<-as.factor(DHS$MaritalStatus_Cat)
table(DHS$MaritalStatus_Cat,DHS$MaritalStatus)
```
## Births in the last 5 years
```{r}
#Check missing values for births in the last 5 years variable
sum(is.na(DHS$Births_Last5Years))
#no missing values

#Check class and levels for births in the last 5 years variable

class(DHS$Births_Last5Years)
levels(DHS$Births_Last5Years)
summary(DHS$Births_Last5Years)


#Recategorize Births Variable

DHS <- DHS %>% 
   mutate(Births_Last5Years_Cat = case_when
                               (Births_Last5Years == "No births" ~ "No Births", 
                                 Births_Last5Years == "1" ~ "1 Birth",
                                 Births_Last5Years == "2"| Births_Last5Years == "3" ~ "2+ Births"))

DHS$Births_Last5Years_Cat<-as.factor(DHS$Births_Last5Years_Cat)
table(DHS$Births_Last5Years_Cat)

#Looks good!

#Re-level
DHS$Births_Last5Years_Cat<- factor(DHS$Births_Last5Years_Cat, levels = c("No Births", "1 Birth", "2+ Births"))
levels(DHS$Births_Last5Years_Cat)
```
## Lifetime sex partners
```{r}
#Check missing values for lifetime sex partners variable
sum(is.na(DHS$SexPartners_Lifetime))
class(DHS$SexPartners_Lifetime)
summary(DHS$SexPartners_Lifetime)
#978 missing values (match with "not had sex" from "FirstSex_Age)

#Check class and levels for lifetime sex partners variable
class(DHS$SexPartners_Lifetime)
levels(DHS$SexPartners_Lifetime)
#Change "NA" values to 0 since these cases did not have sex
DHS$SexPartners_Lifetime<-as.character(DHS$SexPartners_Lifetime)
DHS$SexPartners_Lifetime[is.na(DHS$SexPartners_Lifetime)]= 0
DHS$SexPartners_Lifetime<-as.factor(DHS$SexPartners_Lifetime)
levels(DHS$SexPartners_Lifetime)
summary(DHS$SexPartners_Lifetime)

DHS <- DHS %>% 
   mutate(SexPartnersLifetime_Cat = case_when
                               (SexPartners_Lifetime == "0" ~ "0",
                                SexPartners_Lifetime == "1" 
                                |SexPartners_Lifetime == "2" ~ "1-2",
                                SexPartners_Lifetime == "3" 
                                  |SexPartners_Lifetime == "4" 
                                  | SexPartners_Lifetime == "5"
                                  | SexPartners_Lifetime == "6"
                                  | SexPartners_Lifetime == "7" 
                                  | SexPartners_Lifetime == "8"
                                  | SexPartners_Lifetime == "9"
                                  | SexPartners_Lifetime == "10"
                                  | SexPartners_Lifetime == "11"
                                  | SexPartners_Lifetime == "12"
                                  | SexPartners_Lifetime == "13"
                                  | SexPartners_Lifetime == "15"
                                  | SexPartners_Lifetime == "16"
                                  | SexPartners_Lifetime == "17"
                                  | SexPartners_Lifetime == "18"
                                  | SexPartners_Lifetime == "20"
                                  | SexPartners_Lifetime == "25"
                                  | SexPartners_Lifetime == "30"
                                  | SexPartners_Lifetime == "38"
                                  | SexPartners_Lifetime == "45"
                                  | SexPartners_Lifetime == "59"
                                  | SexPartners_Lifetime == "95+" ~ "3+", 
                                 SexPartners_Lifetime == "Don't know" ~ "Don't Know"))

class(DHS$SexPartnersLifetime_Cat)

DHS$SexPartnersLifetime_Cat<-as.factor(DHS$SexPartnersLifetime_Cat)
# Check it:
table(DHS$SexPartners_Lifetime, DHS$SexPartnersLifetime_Cat)

#Remove the 28 "don't know"
DHS<-DHS %>% 
  filter(SexPartnersLifetime_Cat != "Don't Know")

DHS$SexPartnersLifetime_Cat<- factor(DHS$SexPartnersLifetime_Cat, levels = c("0", "1-2", "3+"))
levels(DHS$SexPartnersLifetime_Cat)
```
## STI in the last 12 months
```{r}
#Check missing values for STI in the last 12 months variable
sum(is.na(DHS$STI_12Months))
#no missing values

#Check class and levels for STI in the last 12 months variable
class(DHS$STI_12Months)
levels(DHS$STI_12Months)
summary(DHS$STI_12Months)

#drop the one "don't know" case
DHS<-DHS %>%
  filter(STI_12Months!= "Don't know")

# get rid of empty "don't know category
DHS$STI_12Months<-factor(DHS$STI_12Months)

levels(DHS$STI_12Months)
```
## Current Contraceptive Method
```{r}
#Check missing values 
sum(is.na(DHS$ContraceptiveMethod_Current))
#no missing values

#Check class and levels for contraceptive method
class(DHS$ContraceptiveMethod_Current)

summary(DHS$ContraceptiveMethod_Current)

#Make contraceptive method categorical and check it
DHS <- DHS %>% 
   mutate(ContraceptiveMethod_Cat = case_when
                               (ContraceptiveMethod_Current == "Male condom"
                                 |ContraceptiveMethod_Current == "Female condom" ~ "Condoms",
                                ContraceptiveMethod_Current == "Not using" ~ "Not Using",
                                ContraceptiveMethod_Current == "Pill" 
                                  | ContraceptiveMethod_Current == "IUD"
                                  | ContraceptiveMethod_Current == "Injections"
                                  | ContraceptiveMethod_Current == "Female sterilization" 
                                  | ContraceptiveMethod_Current == "Male sterilization"
                                  | ContraceptiveMethod_Current == "Periodic abstinence"
                                  | ContraceptiveMethod_Current == "Withdrawal"
                                  | ContraceptiveMethod_Current == "Implants/Norplant"
                                  | ContraceptiveMethod_Current == "Emergency contraception"
                                  | ContraceptiveMethod_Current == "Injections 2 month" ~ "Other Contraceptive"))
DHS$ContraceptiveMethod_Cat<-as.factor(DHS$ContraceptiveMethod_Cat)
table(DHS$ContraceptiveMethod_Cat, DHS$ContraceptiveMethod_Current)
summary(DHS$ContraceptiveMethod_Cat)
```
## Visited a health facility in the last 12 months
```{r}
#Check missing values 
sum(is.na(DHS$HealthFacility_12Months))
#no missing values

#Check class and levels for visit to health facility
class(DHS$HealthFacility_12Months)

summary(DHS$HealthFacility_12Months)
```
## Radio
```{r}
#Check missing values 
sum(is.na(DHS$Radio))
#no missing values

#Check class and levels for radio
class(DHS$Radio)

summary(DHS$Radio)

#Remove cases that are not dejure residents (114 cases)
DHS<-DHS %>% 
  filter(Radio != "Not a dejure resident")
#Remove empty "not a dejure resident" category
DHS$Radio<-factor(DHS$Radio)

levels(DHS$Radio)
summary(DHS$Radio)
```
## TV
```{r}
#Check missing values 
sum(is.na(DHS$TV))
#no missing values (probably because dropped the "not a dejure resident" cases for the Radio variable)

#Check class and levels for TV
class(DHS$TV)

summary(DHS$TV)

DHS$TV<-factor(DHS$TV)
levels(DHS$TV)
```
## Mobile Phone
```{r}
#Check missing values 
sum(is.na(DHS$MobilePhone))
#no missing values

#Check class and levels for Mobile Phone
class(DHS$MobilePhone)

summary(DHS$MobilePhone)
```
## Internet Use
```{r}
#Check missing values 
sum(is.na(DHS$InternetUse))
#no missing values

#Check class and levels for InternetUse
class(DHS$InternetUse)

summary(DHS$InternetUse)

## Make binary
#Make contraceptive method categorical and check it
DHS <- DHS %>% 
   mutate(InternetUse_Cat = case_when
                               (InternetUse == "Never" ~ "Never",
                                 InternetUse == "Yes, last 12 months"
                                 |InternetUse == "Yes, before last 12 months" ~ "Yes"))
DHS$InternetUse_Cat<-as.factor(DHS$InternetUse_Cat)
 #check if it categorized right
table(DHS$InternetUse_Cat,DHS$InternetUse)
```

#Prepare variable set for regression modeling
```{r}
# Check for missing data

#Choose only necessary vars and remove rows with missing data
CompleteDHS <- DHS %>%
  dplyr::select(HIVTest_LastYear, ResidenceType, Age, Age_Cat, Education_Cat, WealthIndex_Cat, MaritalStatus_Cat, Births_Last5Years_Cat, SexPartnersLifetime_Cat, STI_12Months, ContraceptiveMethod_Cat, HealthFacility_12Months, InternetUse_Cat, Radio, TV, MobilePhone, Individual_Weight, Cluster, Stratum) %>%
  drop_na()


MissingRate <-  1- nrow(CompleteDHS)/nrow(DHS)
#Look at missing rate
MissingRate
# Not missing any data
```
#Create Interaction Term
```{r}
#create interaction term to test linearity
CompleteDHS <- CompleteDHS %>%
  mutate(Age_times_logAge = Age * log(Age)) 
```

#Weight variable calculated 
```{r}
#Create weighted variable

CompleteDHS$Weight <- CompleteDHS$Individual_Weight/1000000

# Verify 
names(CompleteDHS)

#Create new var "svydesign" to assign weights for analysis
DHSdesign <- svydesign(id = ~Cluster, strata=~Stratum, weights = ~Weight, data=CompleteDHS)

#Check unweighted contninuous age variable
table(CompleteDHS$Age)

#Check continuous age weighted Frequencies
svytable(~Age, design=DHSdesign)
```
## Boxplots 
```{r}
#Boxplot to assess differences in HIV test by Age (weighted)

svyboxplot(Age~HIVTest_LastYear,design=DHSdesign,col =
             c("mistyrose","powderblue"), xlab="HIV Test", 
                ylab= "Age (years)")

#The median age of participants who never got a HIV test is lower compared to those who got a HIV test. 

#Compare with unweighted boxplots
DHS %>% 
  ggplot(aes(x= HIVTest_LastYear, y = Age)) +
  geom_boxplot(aes(fill =HIVTest_LastYear)) + 
  labs(x = "HIV Test Uptake", y = "Age (years)") + 
  theme_bw()
```
# Univariate Analysis
```{r}
#Run univariate anaysis (binomial logistic regression) using dependent variable (HIVTest) with each independent variable - Variables with statistical signficance satisfy the inclusion criteria for the multivariate logistic regression

lapply(c("ResidenceType", "Age_Cat","Education_Cat", 
         "WealthIndex_Cat", "MaritalStatus_Cat", 
         "Births_Last5Years_Cat", "SexPartnersLifetime_Cat", 
        "STI_12Months",
         "ContraceptiveMethod_Cat","HealthFacility_12Months", 
         "Radio", "TV","MobilePhone","InternetUse_Cat"),
       function(var) {
           formula    <- as.formula(paste("HIVTest_LastYear ~", var))
           univariateCheck <- svyglm(formula, data = DHS, family = binomial, 
                                design=DHSdesign )
           summary(univariateCheck)
       })
#Statistically Significant Variables (P>.05):
#Age_Cat
#MaritalStatus_Cat -"Partnered"
#Birth_Last5Years_Cat -"2+"
#SexPartnersLifetime_Cat
#ContraceptiveMethod_Cat
#HealthFacility_12Months
#MobilePhone

#Non-statistically significant Variables (P<.05)
#Residence_Type, Education, WealthIndex_Cat, STI_Months12, ContraceptiveMethod_Cat, Radio, TV, InternetUse_Cat

#Decision - Include all statistically significant variables (except "FirstSexAge_Cat) in the multivariate analysis. 

#Include the main exposure (ResidenceType), and the following covariates: contraceptive method, mobile phone ownership

#Even though we have non-statistically significant findings at the univariate level, the literature emphasizes the importance to include these variables for  predictive modeling

#Variables will be excluded from the final model if they do not improve model fit
```
# Test linearity assumption
```{r}
#Linearity - assess whether age as a continuous variable is appropriate for the regression models

boxTidwellAGE <- survey::svyglm(HIVTest_LastYear ~ Age + Age_times_logAge, data = CompleteDHS, family = "binomial", design = DHSdesign)

summary(boxTidwellAGE) #interaction term has a p value <0.05 - linearity assumption is violated. Use age categorical variable
```
# Binomial regression
```{r}
#Run logistic regression model
HIVLogitWGHT1<-svyglm(HIVTest_LastYear ~ ResidenceType + Age_Cat+ MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =CompleteDHS, family = "binomial", design=DHSdesign)

ORHIVWGHT1<-exp(cbind(OR = coef(HIVLogitWGHT1), confint(HIVLogitWGHT1))) 
ORHIVWGHT1
```
# Test Assumptions
```{r}
#Assess multicollinearity
vif(HIVLogitWGHT1)
#All variables have a VIF values less than 5 - Assumption is met (no collinearity)

#Cook's D cutoff = 4/2798 
cutoff <- 0.00143

#Influential cases- Cook's D plot [Note: need to run both lines in one setting]
plot(HIVLogitWGHT1, which=4, id.n=5, col= "red")
abline(h=cutoff, lty=2, col="darkred")

#There are 98 influential cases

#identify obs with a Cook's distance greater than the cutoff
obs_no <- as.data.frame(cooks.distance(HIVLogitWGHT1)) %>%
  mutate(obs_no=row_number()) %>%
  filter(`cooks.distance(HIVLogitWGHT1)` > cutoff)

#Exlcude values in the Cook's D plot and compare models
Data_caseremov<-CompleteDHS %>% 
  mutate(CooksD = cooks.distance(HIVLogitWGHT1)) %>% 
  filter(CooksD < cutoff)

#Binomial logistic Regression with influential cases removed
HIVLogitWGHT2<-svyglm(HIVTest_LastYear ~ ResidenceType + Age_Cat+ MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =Data_caseremov, family = "binomial", design=DHSdesign)

ORHIVWGHT2<-exp(cbind(OR = coef(HIVLogitWGHT2), confint(HIVLogitWGHT2))) 
ORHIVWGHT2

#Compare coefficients between models with and without influential observations 
compareCoefs(HIVLogitWGHT1, HIVLogitWGHT2)
#No changes detected, so we can leave all of the cases. 
```
# Run final parsimonious model
```{r}
#Run two logistic regression models 
#Model 1
HIVLogitWGHTPars1<-svyglm(HIVTest_LastYear ~  ResidenceType + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTPars1)

ORHIVWGHTPars1<-exp(cbind(OR = coef(HIVLogitWGHTPars1), confint(HIVLogitWGHTPars1))) 
ORHIVWGHTPars1

#Model 2 - include contraceptive method and mobilephone ownership
HIVLogitWGHTPars2<-svyglm(HIVTest_LastYear ~ ResidenceType + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat  + ContraceptiveMethod_Cat+ HealthFacility_12Months + MobilePhone,data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTPars2)

ORHIVWGHTPars2<-exp(cbind(OR = coef(HIVLogitWGHTPars2), confint(HIVLogitWGHTPars2))) 
ORHIVWGHTPars2

#Pseudo R Squares/Adjusted R Squares
fit.svyglm(HIVLogitWGHTPars1)
fit.svyglm(HIVLogitWGHTPars2)

anova(HIVLogitWGHTPars1, HIVLogitWGHTPars2)

anova(HIVLogitWGHTPars1, HIVLogitWGHTPars2, method="Wald")

AIC(HIVLogitWGHTPars1, HIVLogitWGHTPars2)
BIC (HIVLogitWGHTPars1, HIVLogitWGHTPars2, maximal = HIVLogitWGHTPars2)

#AIC and BIC values for model 1 is lower. This suggests that model 1 is a better fit. 
```
#Test whether wealth index is an effect modifier
```{r}
#Model 1 (with wealth index added)
HIVLogitWGHTWealth<-svyglm(formula =HIVTest_LastYear ~  ResidenceType + WealthIndex_Cat + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTWealth)

ORHIVWGHTWealth<-exp(cbind(OR = coef(HIVLogitWGHTWealth), confint(HIVLogitWGHTWealth))) 
ORHIVWGHTWealth

# model with wealth index * residence type interaction term
HIVLogitWGHTinteraction <- svyglm(HIVTest_LastYear ~  ResidenceType + WealthIndex_Cat + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months + ResidenceType*WealthIndex_Cat, data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTinteraction)

ORHIVLogitWGHTinteraction<-exp(cbind(OR = coef(HIVLogitWGHTinteraction), confint(HIVLogitWGHTinteraction))) 
ORHIVLogitWGHTinteraction

#Interaction Test
anova(HIVLogitWGHTWealth,HIVLogitWGHTinteraction, test = "F", method = "LRT")
#p>0.05,Interaction term is not significant

#Plot interactions
#install.packages("interactions")
library(interactions)

#use cat_plot to plot the interactions

#Visualization 1
cat_plot(HIVLogitWGHTinteraction, pred = ResidenceType, modx = WealthIndex_Cat, 
         geom = "point",
         x.label = "Area of Residence", y.label = "HIV Test in Last Year", legend.main = "Wealth Index")
#No interaction 
```
